Experiments with Synthetic Data

### 2022-07-20 dev/notebooks/synthetic.qmd
more work on streamlingin experiment

```{julia}
# Variables:
μ = 0.1
γ = 0.75
n_rounds = 10
n_folds = 5
T = 1000
```

```{julia}
run_experiment(experiment; n_rounds=n_rounds, μ=μ, n_folds=n_folds, γ=γ, T=T)
```

```{julia}
# Experiments:
experiment = Experiments.Experiment(X,ys,models[:Plugin],target,grid_,n_rounds)
experiment_plugin = Experiments.Experiment(X,ys,models[:Plugin],target,grid_,n_rounds)
experiments = (experiment, experiment_plugin)
```

```{julia}
#| eval: false
using Random, CSV, DataFrames
Random.seed!(1234)
for j in 1:length(generators)
    outcome, path = Experiments.run_experiment(experiments[j], generators[j], n_folds, T=T, store_path=true)
    Experiments.save_path(joinpath(output_path, string(keys(generators)[j])),path)
    CSV.write(joinpath(output_path, string(keys(generators)[j]) * ".csv"), DataFrame(outcome))
end
```

```{julia}
paths = [Experiments.load_path(joinpath(output_path, string(keys(generators)[j]))) for j ∈ 1:length(generators)]
```

```{julia}
function plot_state(path, t; γ=0.75, μ = 0.05, k = 1, length_out=500, size=(150,150), title="")
    chosen = map(p -> p.γ == γ && p.μ == μ && p.t==t && p.k==k, path)
    path = path[chosen][1]
    X = path.X̲'
    y = vec(path.y̲')
    plt = plot_contour(X,y,path.M,length_out=length_out,colorbar=cb,title=title)
    plt = plot(plt, axis=nothing, size=size, legend=false)
end
plot_state(paths[2], 1)
```

```{julia}
#| eval: false
using Main.Experiments: plot_path
paths = [Experiments.load_path(joinpath(output_path, string(keys(generators)[j]))) for j ∈ 1:length(generators)]
anim = Experiments.plot_path(paths[1],Γ=γ,𝙈=μ)
gif(anim,joinpath(www_path,"bayesian.gif"), fps=2)
anim = Experiments.plot_path(paths[2],Γ=γ,𝙈=μ)
gif(anim,joinpath(www_path,"plugin.gif"), fps=2)
```

For the Bayesian classifier with greedy recourse...

![](www/synthetic/bayesian.gif)

For the non-Bayesian classifier with generic recourse...

![](www/synthetic/plugin.gif)

```{julia}
using Main.Experiments: prepare_results, plot_results
validity = DataFrame()
cost = DataFrame()
files = (Bayesian=joinpath(output_path, "Bayesian.csv"), Plugin=joinpath(output_path, "Plugin.csv"))
results = map(file -> CSV.read(file, DataFrame), files)
p_val, p_cost = plot_results(results);
```

```{julia}
p_val
```

```{julia}
p_cost
```

## Neural network

```{julia}
using Flux
data = Models.prepare_data(X', y')
nn = Models.build_model(input_dim=size(X')[1], n_hidden=100)
loss(x, y) = Flux.Losses.logitbinarycrossentropy(nn(x), y);
```

Training a single neural network...

```{julia}
using BSON
run = false
opt = ADAM()
if run
  # Train model:
  using Flux.Optimise: update!, ADAM
  using Statistics, StatsBase
  epochs = 10
  avg_loss(data) = mean(map(d -> loss(d[1],d[2]), data))
  accuracy(data) = sum(map(d ->round.(Flux.σ.(nn(d[1]))) .== d[2], data))[1]/length(data)

  using Plots
  anim = Animation()
  avg_l = [avg_loss(data)]
  p1 = scatter(ylim=(0,avg_l[1]), xlim=(0,epochs), legend=false, xlab="Epoch", title="Average loss")
  acc = [accuracy(data)]
  p2 = scatter(ylim=(0.5,1), xlim=(0,epochs), legend=false, xlab="Epoch", title="Accuracy")

  τ = 1.1
  stopping_criterium_reached = accuracy(data) >= τ
  epoch = 1

  while epoch <= epochs && !stopping_criterium_reached
    for d in data
      gs = gradient(Flux.Flux.params(nn)) do
        l = loss(d...)
      end
      update!(opt, Flux.Flux.params(nn), gs)
    end
    avg_l = vcat(avg_l,avg_loss(data))
    plot!(p1, [0:epoch], avg_l, color=1)
    scatter!(p1, [0:epoch], avg_l, color=1)
    acc = vcat(acc,accuracy(data))
    plot!(p2, [0:epoch], acc, color=1)
    scatter!(p2, [0:epoch], acc, color=1)
    plt=plot(p1,p2, size=(600,300))
    frame(anim, plt)

    # Check if desired accuracy reached:
    stopping_criterium_reached = accuracy(data) >= τ

    epoch += 1

  end

  gif(anim, joinpath(www_path
, "single_nn.gif"), fps=10)

  BSON.@save joinpath(output_path
, "nn.bson") nn

end
```

```{julia}
using BSON: @load
@load joinpath(output_path, "nn.bson") nn
Mₙₙ = Models.FittedNeuralNet(nn, opt, loss);
```

Training a deep ensemble...

```{julia}
opt = ADAM()
loss_type = :logitbinarycrossentropy
run = false
if run
    K = 50
    ensemble = Models.build_ensemble(K,kw=(input_dim=size(X')[1], n_hidden=100));
    ensemble, anim = Models.forward(ensemble, data, opt, n_epochs=10, plot_every=10, loss_type=loss_type, τ=1.1); # fit the ensemble
    Models.save_ensemble(ensemble, root=joinpath(output_path
, "ensemble")) # save to disk
    gif(anim, joinpath(www_path
, "ensemble_loss.gif"), fps=25);
end
```

```{julia}
ensemble = Models.load_ensemble(root=joinpath(output_path, "ensemble"))
M = Models.FittedEnsemble(ensemble, opt, loss_type)
models = (Bayesian=M, Plugin=Mₙₙ);
```

```{julia}
using Main.Experiments: plot_contour
p1 = plot_contour(X,y,models[1],title="Bayesian")
p2 = plot_contour(X,y,models[2],title="Plugin")
plot(p1,p2,size=(1000,400))
```

```{julia}
# Experiments:
experiment = Experiments.Experiment(X',y',models[:Plugin],target,grid_,n_rounds)
experiment_plugin = Experiments.Experiment(X',y',models[:Plugin],target,grid_,n_rounds)
experiments = (experiment, experiment_plugin);
```

```{julia}
run = true
if run
    using Random
    Random.seed!(1234)
    for j in 1:length(generators)
        outcome, path = Experiments.run_experiment(experiments[j], generators[j], n_folds, T=T, store_path=true)
        Experiments.save_path(joinpath(output_path
    , string(keys(generators)[j])),path)
        CSV.write(joinpath(output_path
    , string(keys(generators)[j]) * "_deep.csv"), DataFrame(outcome))
    end
end
```

>>>>

```{julia}
# Variables:
μ = 0.1
γ = 0.75
n_rounds = 2
n_folds = 5
T = 1000
```

```{julia}
output = run_experiment(experiment; n_rounds=n_rounds, μ=μ, n_folds=n_folds, γ=γ, T=T)
```

```{julia}
using CSV, BSON
CSV.write(joinpath(output_path,"synthetic_data.csv"), output)
BSON.@save joinpath(output_path,"synthetic_data.bson") output
```
